The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-06-24 paper/paper.tex
add new plots

@@

A comparison of trained-edge and fixed-edge methods on the CosmoDC2 griz scenarios
is shown in Figure \ref{fig:edges}.  One important point to note is that while trained-edge
methods dominate the highest scores for the 3x2pt DETF metric, on which they trained, they
fare much worse on the lensing-only metrics (the methods were not re-trained on the lensing metrics;
we show the metrics for the same assigned bins).  This suggests that the difference between
optimal bins for different science cases is a significant one, and thus that analysis pipelines
should make it straightforward to calibrate multiple configurations and pass them to
subsequent science anlysis; this will probably be true even when comparing models
differing only in their systematic parametrizations.  
This feature is highlighted by the comparison between the two variants
of the \textsc{NeuralNetwork} entry, which differed only in which metric they were targeting;
optimizing one metric does not optimize the other.

@@

@@

>>>>

An illustration of the rank acheived by each method within each challenge configuration and for each metric
is shown in \autoref{fig:rank_grid}.

\begin{figure*}[htbp]
	% \centering
	\includegraphics[width=\linewidth]{results/rank_grid.pdf}
	\caption{The rank of each method (1 = highest scoring, 25 = lowest scoring) within each configuration of the challenge, for each metric separately.  A method that was good everywhere would appear as yellow strip across an entire horizontal range.}
	\label{fig:rank_grid}
\end{figure*}

@@

A comparison of trained-edge and fixed-edge methods on the CosmoDC2 griz scenarios
is shown in Figure \ref{fig:edges}, and the same data normalized against the score acheived
by objects binned in true redshift (i.e. a perfect assigment method) are shown in Figure \ref{fig:metric_grid_dc2_griz}.

One important point to note is that while trained-edge
methods dominate the highest scores for the 3x2pt DETF metric, on which they trained, they
fare much worse on the lensing-only metrics (the methods were not re-trained on the lensing metrics;
we show the metrics for the same assigned bins).  This suggests that the difference between
optimal bins for different science cases is a significant one, and thus that analysis pipelines
should make it straightforward to calibrate multiple configurations and pass them to
subsequent science anlysis; this will probably be true even when comparing models
differing only in their systematic parametrizations.  
This feature is highlighted by the comparison between the two variants
of the \textsc{NeuralNetwork} entry, which differed only in which metric they were targeting;
optimizing one metric does not optimize the other.

@@

\begin{figure*}
\includegraphics[width=1\linewidth]{results/metric_grid_dc2_griz.pdf}
\caption{Normalized scores for each method, normalized between the score for random assignment (zero) and truth assignment to bins with equal number counts (one).  It can be seen that both equal-number and equal-redshift spacings can be beaten for certain metrics.  In each case, classification is done using griz bands on the CosmoDC2 data set; equivalent plots for Buzzard and riz are shown in \autoref{app:metric_grids}.}
\label{fig:metric_grid_dc2_griz}
\end{figure*}

@@

\section{Normalized metric scores} \label{app:metric_grids}
Figures \ref{fig:metric_grid_dc2_riz}, \ref{fig:metric_grid_buzzard_griz}, and \ref{fig:metric_grid_buzzard_riz} show metric scores normalized bewteen random assignment and perfect assignemtn to equal number density bins for CosmoDC2/riz, Buzzard/griz and Buzzard/riz respectively

\begin{figure*}
\includegraphics[width=1\linewidth]{results/metric_grid_dc2_riz.pdf}
\caption{Normalized scores for each method, following the scheme of Figure \ref{fig:metric_grid_dc2_griz}
but for CosmoDC2 with riz bands}
\label{fig:metric_grid_dc2_riz}
\end{figure*}

\begin{figure*}
\includegraphics[width=1\linewidth]{results/metric_grid_buzzard_griz.pdf}
\caption{Normalized scores for each method, following the scheme of Figure \ref{fig:metric_grid_dc2_griz}
but for Buzzard with griz bands}
\label{fig:metric_grid_buzzard_griz}
\end{figure*}

\begin{figure*}
\includegraphics[width=1\linewidth]{results/metric_grid_buzzard_riz.pdf}
\caption{Normalized scores for each method, following the scheme of Figure \ref{fig:metric_grid_dc2_griz}
but for Buzzard with riz bands}
\label{fig:metric_grid_buzzard_riz}
\end{figure*}
